---
title: "Celltype identification of clustered WNN, CCA integrated data"
author: "Julius Lautenbach"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_notebook:
    self_contained: yes
    highlight: tango
    df_print: paged
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
    toc_depth: 3
  html_document:
    self_contained: yes
    highlight: tango
    df_print: paged
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
    toc_depth: 3
    keep_md: yes
    fig_caption: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_knit$set(echo = TRUE, root.dir = getwd(), fig.width = 6, fig.height = 5, warning = FALSE, message = FALSE)

result.dir <- paste0("../results/",Sys.Date(),"/")

## creates result.dir with date in if not existent
ifelse(isFALSE(dir.exists(paste0("../",result.dir))), dir.create(paste0("../",result.dir),recursive = TRUE),"Result directory for today exists already!")
options(stringsAsFactors = FALSE)
```

# Libraries
```{r message = FALSE}
library(tidyverse)
library(data.table)
library(Seurat)
library(patchwork)
library(randomcoloR)
source("../helper_fun.R")
#install.packages("clustree")
library(clustree) ## see https://cran.r-project.org/web/packages/clustree/vignettes/clustree.html for explanation
mapal <- colorRampPalette(RColorBrewer::brewer.pal(11,"RdBu"))(256)
```


## change color
```{r}
names(ENDEMIC_colors) <- c("previously","primary")
```


```{r}
#adt_rna <- readRDS("../../data/SeuratObjects/2021-12-10AbSeq_Cell_Calling_qc_cca_wnn.rds")
#adt_rna <- readRDS("../../data/SeuratObjects/2021-12-13AbSeq_Cell_Calling_qc_cca_wnn_clustering.rds")
adt_rna <- readRDS("../../data/RhapsodyCountFiles/temp/AbSeq_Cell_Calling_qc_cca_wnn_clustering.rds")

```

## Background information for loaded Seurat Object
* Seurat object containing 12 samples, from 4 libraries
* Doublets and undetermined cells, determined by BD SevenBridges pipline, were removed
* Only cells with "min.cells = 3" and "min.features = 10" on RNA level were included

### QC step removed cells with based on RNA counts
resulting in 374 genes across 73,121 cells

### Data integration
* CCA integrated (horizontal integration, 12-sample integration, for each modality)
* WNN integratd (vertical integration, 2-layer integration, rna and adt)

#### CCA ingetration - RNA
* logNormalized, scale.factor=10000
* dim 1:30

#### CCA ingetration - ADT
* CLR noralization, margin=2
* dim 1:18

#### WNN integration
* "rna.cca.pca", "adt.cca.pca"
* list(1:30, 1:18)
* prune.SNN = 1/15, # default Cutoff not to discard edge in SNN graph
* k.nn = 20, ## default the number of multimodal neighbors to compute
* knn.range = 200, ## default The number of approximate neighbors to compute


### Clustering on WNN integrated graph with "smart local moving (SLM) algorithm"
* SLM algorithm - graph-based smart local moving (SLM) algorithm (Waltman and Van Eck, 2013)
-> "wsnn_res.0.8" suggested by seurat

```{r}
adt_rna@meta.data %>% select(contains("wsnn_res")) %>% names() ## seurat default clustering number
```

* algorithm 3
* SLM algorithm - graph-based smart local moving (SLM) algorithm (Waltman and Van Eck, 2013)
* resolution calculated c(0.01,0.05,0.1,0.2,0.25,0.3,0.4,0.5,1,2)

### evalutation of clustering

```{r fig.width=6, fig.height=4}
clustree(adt_rna@meta.data, prefix = "wsnn_res.")
```

## Comment: resolution of at least 0.8 seems best for CCA(ADT+RNA)-WNN


```{r fig.width=7, fig.height=2}
Idents(adt_rna) <- "wsnn_res.0.01"

p1 <- DimPlot(adt_rna, reduction = 'wnn.umap', label = TRUE, repel = TRUE, label.size = 2.5) + NoLegend() + ggplot2::ggtitle("wsnn_res.0.01")

Idents(adt_rna) <- "wsnn_res.0.05"

p2 <- DimPlot(adt_rna, reduction = 'wnn.umap', label = TRUE, repel = TRUE, label.size = 2.5) + NoLegend()+ ggplot2::ggtitle("wsnn_res.0.05")

Idents(adt_rna) <- "wsnn_res.0.1"

p3 <- DimPlot(adt_rna, reduction = 'wnn.umap', label = TRUE, repel = TRUE, label.size = 2.5) + NoLegend() + ggplot2::ggtitle("wsnn_res.0.1")

Idents(adt_rna) <- "wsnn_res.0.8"

p4 <- DimPlot(adt_rna, reduction = 'wnn.umap', label = TRUE, repel = TRUE, label.size = 2.5) + NoLegend()+ ggplot2::ggtitle("wsnn_res.0.8")

p1 | p2 | p3 | p4
```


### Normalizing unintegrated data

```{r}
pbmc <- adt_rna
#- RNA Normalization
pbmc <- NormalizeData(object = pbmc, assay = 'RNA', normalization.method = 'LogNormalize', scale.factor = 10000) %>% ScaleData(vars.to.regress = "nCount_RNA")

#- Ab Normalization
pbmc <- NormalizeData(object = pbmc, assay = 'ADT', normalization.method = 'CLR') %>% ScaleData() #margin   If performing CLR normalization, normalize across features (1) or cells (2)


pbmc@meta.data$wsnn_res.0.8num <- as.numeric(as.character(pbmc@meta.data$wsnn_res.0.8))
```

### Finding conserved markers for each clusters
* on un-integrated data
* might help cell type identification
```{r message=FALSE, warning=FALSE}
Idents(pbmc) <- "wsnn_res.0.8"
DefaultAssay(pbmc) <- "RNA"
cluster.marker.list <- list()

for(cluster in unique(pbmc@meta.data$wsnn_res.0.8)){
  markers <-
    FindConservedMarkers(pbmc,ident.1 = cluster, grouping.var = "orig.ident", verbose = FALSE)
  cluster.marker.list[[cluster]] <- markers
}
```
```{r}
conserved.markers <- bind_rows(cluster.marker.list, .id = 'cluster') %>%
  rownames_to_column("gene") %>% mutate(gene = gsub("\\..*","",gene))

#conserved.markers %>% group_by(cluster) %>% count(cluster)
#conserved.markers %>% group_by(cluster) %>% arrange(max_pval)
conserved.markers1 <- conserved.markers %>%
  group_by(cluster) %>%
  top_n(n = 3, wt = desc(max_pval)) #%>% ungroup()

conserved.markers1 %>% arrange(as.numeric(cluster))
```


```{r}
Idents(pbmc) <- "wsnn_res.0.8num"
DimPlot(pbmc, reduction = 'wnn.umap', label = TRUE, repel = TRUE, label.size = 5) + NoLegend() + ggplot2::ggtitle("wsnn_res.0.8")
```

```{r}
DefaultAssay(pbmc) <- "rna.CCA"#"RNA.CCA"
DoHeatmap(subset(x = pbmc, downsample = 100),# Downsample the number of cells per identity class
          features = c(conserved.markers1$gene), assay = "rna.CCA",label = T,group.by = "wsnn_res.0.8num") + NoLegend() + ggplot2::ggtitle("mRNA markers") + scale_fill_gradientn(colours = rev(mapal)) + theme(text = element_text(size = 6))
```


```{r}
## ADT
DefaultAssay(pbmc) <- "adt.CCA"#"RNA.CCA"
DoHeatmap(subset(x = pbmc, downsample = 100),# Downsample the number of cells per identity class
          features = rownames(pbmc),group.by = "wsnn_res.0.8num",
          size = 2) + NoLegend() +ggplot2::ggtitle("Protein markers") + scale_fill_viridis()
```

## Level 1 Cell type

Level 1 annotations: CD4+ T cells, CD8+ T cells, Unconventional T, B cells, Natural Killer (NK) cells, Monocytes, Dendritic Cells (DC), and Other (consisting of progenitors and additional rare populations expressing erythroid or platelet lineage markers)

```{r}
l1.cluster.ids <- c("0" = "Monocytes",
                    "1" = "NK",
                    "2" = "CD4+ T",
                    "3" = "NK",
                    "4" = "CD4+ T",
                    "5" = "CD4+ T",
                    "6" = "CD4+ T",
                    "7" = "Monocytes",
                    "8" = "CD8+ T",
                    "9" = "CD8+ T",
                    "10" = "CD8+ T",
                    "11" = "gdT",
                    "12" = "undefined",
                    "13" = "CD8+ T",
                    "14" = "Monocytes",
                    "15" = "CD4+ T", #CD€/CD8 mix
                    "16" = "B",
                    "17" = "CD4+ T",
                    "18" = "B",
                    "19" = "CD4+ T",
                    "20" = "NK",
                    "21" = "gdT",
                    "22" = "CD4+ T",
                    "23" = "NK",
                    "24" = "CD4+ T",
                    "25" = "DC",
                    "26" = "CD8+ T",
                    "27" = "Monocytes",
                    "28" = "DC",
                    "29" = "B",
                    "30" = "CD4+ T",
                    "31" = "CD4+ T"
                    #"32" = "?"
                    )
l1.cluster.ids.colors <- randomcoloR::distinctColorPalette(length(l1.cluster.ids))
names(l1.cluster.ids.colors) <- l1.cluster.ids

pbmc <- RenameIdents(pbmc, l1.cluster.ids)
pbmc$CellType_L1 <- Idents(pbmc)
Idents(pbmc) <- "wsnn_res.0.8"
DimPlot(pbmc, reduction = "wnn.umap",cols = l1.cluster.ids.colors, group.by = "CellType_L1",repel = T,label = T, pt.size = 0.5)
```

```{r}
library(scales)

tibble(pbmc@meta.data) %>%
  group_by(Time,orig.ident) %>%
  count(CellType_L1) %>%
  # Stacked + percent
  ggplot(aes(fill = CellType_L1, y=n, x=orig.ident)) +
  geom_bar(position="fill", stat="identity",width = 0.9) +
  scale_fill_manual(values = l1.cluster.ids.colors) +
  facet_grid(~Time,scales = "free_x") +
  scale_y_continuous(labels = percent) + ## labels requires package scales
  labs(x = "",
       y = "Percentage") +
  theme_cowplot() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

```

### Level 1 all clusters, 100 cells
```{r message=FALSE, warning=FALSE}
## ADT
DefaultAssay(pbmc) <- "adt.CCA"#"RNA.CCA"
# Downsample the number of cells per identity class
DoHeatmap(subset(x = pbmc, downsample = 100,cells = colnames(pbmc)[pbmc@meta.data$wsnn_res.0.8num %in% c(0:10)]),
          features = rownames(pbmc),group.by = "wsnn_res.0.8num",
          size = 2) + NoLegend() +ggplot2::ggtitle("Protein markers") + scale_fill_viridis()
DoHeatmap(subset(x = pbmc, downsample = 100,cells = colnames(pbmc)[pbmc@meta.data$wsnn_res.0.8num %in% c(10:20)]),
          features = rownames(pbmc),group.by = "wsnn_res.0.8num",
          size = 2) + NoLegend() +ggplot2::ggtitle("Protein markers") + scale_fill_viridis()
DoHeatmap(subset(x = pbmc, downsample = 100,cells = colnames(pbmc)[pbmc@meta.data$wsnn_res.0.8num %in% c(20:32)]),
          features = rownames(pbmc),group.by = "wsnn_res.0.8num",
          size = 2) + NoLegend() +ggplot2::ggtitle("Protein markers") + scale_fill_viridis()
```

### Level 1 CD4+ and CD8+ T cells
```{r message=FALSE, warning=FALSE}
## ADT
DefaultAssay(pbmc) <- "adt.CCA"#"RNA.CCA"
# Downsample the number of cells per identity class
 DoHeatmap(subset(x = pbmc, #downsample = 100,
                 cells = colnames(pbmc)[pbmc@meta.data$CellType_L1 %in% c("CD4+ T","undefined")]),
          features = rownames(pbmc),group.by = "wsnn_res.0.8num",
          size = 2) + NoLegend() + ggplot2::ggtitle("CD4+ Protein markers") + scale_fill_viridis()

DoHeatmap(subset(x = pbmc, #downsample = 100,
                 cells = colnames(pbmc)[pbmc@meta.data$CellType_L1 %in% c("CD8+ T","undefined")]),
          features = rownames(pbmc),group.by = "wsnn_res.0.8num",
          size = 2) + NoLegend() + ggplot2::ggtitle("CD8+ Protein markers") + scale_fill_viridis()
```

### Level 1 NK an gdT cells
```{r message=FALSE, warning=FALSE}
## ADT
DefaultAssay(pbmc) <- "adt.CCA"#"RNA.CCA"
# Downsample the number of cells per identity class
DoHeatmap(subset(x = pbmc, #downsample = 100,
                           cells = colnames(pbmc)[pbmc@meta.data$CellType_L1 %in% c("NK")]),
          features = rownames(pbmc),group.by = "wsnn_res.0.8num",
          size = 2) + NoLegend() + ggplot2::ggtitle("NK Protein markers") + scale_fill_viridis()

DoHeatmap(subset(x = pbmc, #downsample = 100,
                           cells = colnames(pbmc)[pbmc@meta.data$CellType_L1 %in% c("gdT")]),
          features = rownames(pbmc),group.by = "wsnn_res.0.8num",
          size = 2) + NoLegend() + ggplot2::ggtitle("gdT Protein markers") + scale_fill_viridis()
```

### Level 1 Monocytes
```{r message=FALSE, warning=FALSE}
## ADT
DefaultAssay(pbmc) <- "adt.CCA"#"RNA.CCA"
# Downsample the number of cells per identity class
DoHeatmap(subset(x = pbmc, downsample = 100,cells = colnames(pbmc)[pbmc@meta.data$CellType_L1 %in% c("Monocytes")]),
          features = rownames(pbmc),group.by = "wsnn_res.0.8num",
          size = 2) + NoLegend() + ggplot2::ggtitle("Monocytes Protein markers") + scale_fill_viridis()
```

#### Subclustering of cluster 12
```{r}
Idents(pbmc) <- "wsnn_res.0.8"

pbmc <- FindSubCluster(pbmc,cluster=12,subcluster.name = "Subclustering_12",graph.name = "wsnn",algorithm = 3,resolution = 0.1)
```

```{r message=FALSE, warning=FALSE}
## ADT
DefaultAssay(pbmc) <- "adt.CCA"#"RNA.CCA"
# Downsample the number of cells per identity class
DoHeatmap(subset(x = pbmc, #downsample = 100,
                 cells = colnames(pbmc)[grepl("12_",pbmc@meta.data$Subclustering_12)]),
          features = rownames(pbmc),group.by = "Subclustering_12",
          size = 2) + NoLegend() + ggplot2::ggtitle("cluster12 Protein markers") + scale_fill_viridis()

DefaultAssay(pbmc) <- "rna.CCA"#"RNA.CCA"
# Downsample the number of cells per identity class
DoHeatmap(ScaleData(subset(x = pbmc, #downsample = 100,
                           cells = colnames(pbmc)[grepl("12_",pbmc@meta.data$Subclustering_12)])),
          features = conserved.markers1$gene, assay = "rna.CCA",label = T,group.by = "Subclustering_12") + NoLegend() + ggplot2::ggtitle("mRNA markers") + scale_fill_gradientn(colours = rev(mapal)) + theme(text = element_text(size = 6))

```

#### Subclustering of cluster 15
```{r}
Idents(pbmc) <- "wsnn_res.0.8"

pbmc <- FindSubCluster(pbmc,cluster=15,subcluster.name = "Subclustering_15",graph.name = "wsnn",algorithm = 3,resolution = 0.2)
```

```{r message=FALSE, warning=FALSE}
## ADT
DefaultAssay(pbmc) <- "adt.CCA"#"RNA.CCA"
# Downsample the number of cells per identity class
DoHeatmap(subset(x = pbmc, #downsample = 100,
                 cells = colnames(pbmc)[grepl("15_",pbmc@meta.data$Subclustering_15)]),
          features = rownames(pbmc),group.by = "Subclustering_15",
          size = 2) + NoLegend() + ggplot2::ggtitle("cluster15 Protein markers") + scale_fill_viridis()

DefaultAssay(pbmc) <- "rna.CCA"#"RNA.CCA"
# Downsample the number of cells per identity class
DoHeatmap(ScaleData(subset(x = pbmc, #downsample = 100,
                           cells = colnames(pbmc)[grepl("15_",pbmc@meta.data$Subclustering_15)])),
          features = conserved.markers1$gene,
          assay = "rna.CCA",label = T,group.by = "Subclustering_15") + NoLegend() + ggplot2::ggtitle("mRNA markers") + scale_fill_gradientn(colours = rev(mapal)) + theme(text = element_text(size = 6))
```

### DEG for all clusters
```{r}
Idents(pbmc) <- "wsnn_res.0.8"
all.adt.markers <- FindAllMarkers(pbmc,assay="adt.CCA")
all.rna.markers <- FindAllMarkers(pbmc,assay="rna.CCA")

## pvalues don't matter here, fold-change is sufficient for identification
adt.markers <- all.adt.markers %>%
  group_by(cluster) %>%
  top_n(n = 5, wt = abs(avg_log2FC)) %>% ungroup()

rna.markers <- all.rna.markers %>%
  group_by(cluster) %>%
  top_n(n = 5, wt = abs(avg_log2FC)) %>% ungroup()
```


### Level 1 transcriptome CD4+ and CD8+ T cells
```{r message=FALSE, warning=FALSE}
## ADT
DefaultAssay(pbmc) <- "rna.CCA"#"RNA.CCA"
# Downsample the number of cells per identity class
 DoHeatmap(subset(x = pbmc, #downsample = 100,
                 cells = colnames(pbmc)[pbmc@meta.data$CellType_L1 %in% c("CD4+ T")]),
          features = rna.markers$gene, group.by = "wsnn_res.0.8num",
          size = 2) + NoLegend() + ggplot2::ggtitle("CD4+ T cells mRNA markers") + scale_fill_gradientn(colours = rev(mapal)) + theme(text = element_text(size = 6))

DoHeatmap(subset(x = pbmc, #downsample = 100,
                 cells = colnames(pbmc)[pbmc@meta.data$CellType_L1 %in% c("CD8+ T")]),
          features = rna.markers$gene, group.by = "wsnn_res.0.8num",
          size = 2) + NoLegend() + ggplot2::ggtitle("CD8+ T cells mRNA markers") + scale_fill_gradientn(colours = rev(mapal)) + theme(text = element_text(size = 6))
```

## Level 2 Cell type

30 Level 2 annotation categories representing well-described subtypes of human immune cells: CD4+ T Naive, CD4+ T Central Memory (TCM), CD4+ T Effector Memory (TEM), CD8+ TEM, etc., all thirty subtypes are listed at https://azimuth.hubmapconsortium.org/).

```{r message=FALSE, warning=FALSE, fig.asp=0.5}
l2.cluster.ids <- c("0" = "CD14+ monocytes",# S100A12,TGFBI, CD36 classical mono, TGFBI classical/non-classical
                    "1" = "NK1",
                    "2" = "CD4+ T naive",#"CD4 CD45RA, CD27, CD197", #	LEF1 naive? CCR7 naive, PIK3IP1 naive
                    "3" = "NK2",
                    "4" = "CD4+ Tfh", ## CD4, CXCR5+, CD27 but CD45RA neg -> central memory cells #,"CD4 CD27 CXCR5"
                    "5" = "CD4+ T central memory",#"CD4 CD27 CD25/CD197",#  CD25 is IL2R or something, CD27, CCR7, low CD45RA -> central memory
                    "6" = "CD4+ T transitional memory", # noCCR7 -> effector,
                    "7" = "CD16+ monocytes",#SLC7A7 non-classical, CXCL16 non-classical,C1QA intermediate/non-classical# ## non classical monocytes; low CD14, high CD16, CD11c+ HLADR+, CD123 medium
                    "8" = "CD8+ T naive",#"CD8 CD197 CD27 CD45RA", ## similar to CD4 cluster 2
                    "9" = "CD8+ T effector memory",
                    "10" = "CD8+ T transitional memory",
                    "11" = "Vd2+ gdT",
                    "12" = "undefined",
                    "13" = "CD8+ NKT", ## CD56 #CD8, CD56 should express Valpha24 mrna?
                    "14" = "CD14+ monocytes",
                    "15" = "CD4+ T activated effector", #KIAA0101 memory treg? TOP2A treg,TYMS memory treg
                    "16" = "B memory", # CD80+, , #https://www.nature.com/articles/ni.2914
                    "17" = "CD4+ T transitional memory", #HLADR-
                    "18" = "B Naive", #CD27-
                    "19" = "CD4+ T regulatory CD80-",
                    "20" = "NK3",
                    "21" = "Vd2- gdT",
                    "22" = "CD4+ T regulatory CD80+", # Treg
                    "23" = "NK4",
                    "24" = "CD4+ T effector memory",
                    "25" = "mDC",#"DC CD123 HLADR CD11c", CD34− HLA−DR+ CD123low CD11c+
                    "26" = "CD8+ Tfh", ## "CD8 cd27 cxcr5", CD8+, CXCR5+,CD80+(co-stimmulatory moleucle for Tcells) CD27 but CD45RA neg -> central memory (check mrna SELL/CD62L/L-Selectin) - CD27/CX3/CR1/SELL/CD28 gerlach nomenclature for tcell subcells# similar to cd4 cluster 4 # GZMK Memory CD4 T-cell Th1/Th17
                    "27" = "CD14+ monocytes",
                    "28" = "pDC",
                    "29" = "Plasma cells", # CD27+
                    "30" = "CD4+ T naive",
                    "31" = "CD4+ T naive"#,#"CD4 CD45RA, CD27, CD197",
                    #"32" = "undefined"
                    )
Idents(pbmc) <- "wsnn_res.0.8"
l2.cluster.ids.colors <- randomcoloR::distinctColorPalette(length(l2.cluster.ids))
names(l2.cluster.ids.colors) <- l2.cluster.ids

pbmc <- RenameIdents(pbmc, l2.cluster.ids)
pbmc$CellType_L2 <- Idents(pbmc)

Idents(pbmc) <- "wsnn_res.0.8"
DimPlot(pbmc, reduction = "wnn.umap",cols = l2.cluster.ids.colors,
        group.by = "CellType_L2", repel = T,label = T, pt.size = 0.75)
```

#### Reordering/Data wrangling
```{r}
pbmc$CellType_L2B <- paste0(pbmc$wsnn_res.0.8num,": ",pbmc$CellType_L2)
pbmc@meta.data %>% select(CellType_L2,CellType_L2B)

pbmc <- AddMetaData(pbmc, pbmc@meta.data %>%
  rownames_to_column("CellID") %>%
  arrange(CellType_L1, wsnn_res.0.8num) %>%               # sort your dataframe
  mutate(CellType_L2B = factor(CellType_L2B, unique(CellType_L2B)),
         CellType_L2 = factor(CellType_L2, unique(CellType_L2))) %>% # reset your factor-column based on that order
  #mutate(CellType_L2num = as.numeric(CellType_L2)-1) %>%
  column_to_rownames("CellID"))

#pbmc@meta.data <- pbmc@meta.data %>%
#  rownames_to_column("CellID") %>%
#  arrange(CellType_L1, wsnn_res.0.8num) %>%               # sort your dataframe
#  mutate(CellType_L2B = factor(CellType_L2B, unique(CellType_L2B)),
#         CellType_L2 = factor(CellType_L2, unique(CellType_L2))) %>% # reset your factor-column based on that order
#  #mutate(CellType_L2num = as.numeric(CellType_L2)-1) %>%
#  column_to_rownames("CellID")

pbmc@meta.data %>% select(CellType_L2,CellType_L2B)

```
#### UMAP plotting
```{r fig.asp=0.5}
Idents(pbmc) <- "wsnn_res.0.8"

plot1 <- DimPlot(pbmc, reduction = "wnn.umap", group.by = "CellType_L2",cols = l2.cluster.ids.colors, repel = T, label = F,pt.size = 0.1) +
  #NoLegend() +
  labs(title = "Immune landscape")

LabelClusters(plot1, id = "CellType_L2", color = unique(ggplot_build(plot1)$data[[1]]$colour), size = 2, repel = T,  box.padding = 1,max.overlaps=100)

```

```{r }
Idents(pbmc) <- "wsnn_res.0.8"

plot1 <- DimPlot(pbmc, reduction = "wnn.umap", group.by = "CellType_L2",cols = l2.cluster.ids.colors, repel = T, label = F,pt.size = 0.1) +
  NoLegend() +
  labs(title = "Immune landscape")

LabelClusters(plot1, id = "CellType_L2", color = unique(ggplot_build(plot1)$data[[1]]$colour), size = 2, repel = T,  box.padding = 1,max.overlaps=100)
```
```{r }
Idents(pbmc) <- "wsnn_res.0.8"

plot1 <- DimPlot(pbmc, reduction = "wnn.umap", group.by = "CellType_L2", repel = T, label = F,pt.size = 0.1) +
  NoLegend() +
  labs(title = "Immune landscape")

LabelClusters(plot1, id = "CellType_L2", color = "black", size = 2.5, repel = T,  box.padding = 1,max.overlaps=100)
```

### alternative (ggplot2) UMAP

```{r message=FALSE, warning=FALSE}
umap_data_ggplot <- data.table(pbmc@meta.data,
                               Embeddings(object = pbmc, reduction = 'wnn.umap')) %>%
  rownames_to_column("CellID") %>%
  arrange(CellType_L1, wsnn_res.0.8num) %>%               # sort your dataframe
  mutate(CellType_L2B = factor(CellType_L2B, unique(CellType_L2B)),
         CellType_L2 = factor(CellType_L2, unique(CellType_L2))) # reset your factor-column based on that order

plot_UMAP <- ggplot(umap_data_ggplot %>%arrange(sample(x = CellID, replace = FALSE)), ## arrange(CellType_L1,wsnn_res.0.8num) %>%
                    aes(x = wnnUMAP_1, y = wnnUMAP_2)) +
  theme(axis.text = element_blank(), axis.ticks = element_blank())

#- Batch
plot_UMAP + geom_point(aes(color = as.character(orig.ident)), size = 0.1) +
  labs(x = 'UMAP 1', y = 'UMAP 2',subtitle = "Sample") + scale_color_discrete(guide = FALSE) + theme_cowplot() #theme_minimal()

#- Time
plot_UMAP + geom_point(aes(color = as.character(Time)), size = 0.1) +
  labs(x = 'UMAP 1', y = 'UMAP 2',subtitle = "Sample Time Point") + scale_color_discrete(guide = FALSE) + theme_cowplot()

#- Batch per Time
plot_UMAP + geom_point(aes(color = as.character(Library)), size = 0.1) +
  labs(x = 'UMAP 1', y = 'UMAP 2',subtitle = "Patient") + scale_color_discrete(guide = FALSE) + facet_grid(~Time) +theme_cowplot()
```

### In-silico bulk analysis
* on CCA integrated data
* per Timepoint, Group

```{r fig.asp=0.5}
DefaultAssay(pbmc) <- "rna.CCA"
# How can I calculate expression averages separately for each replicate?
cluster.averages <- AverageExpression(pbmc, return.seurat = TRUE, group.by = c("Time","Group"))

# You can also plot heatmaps of these 'in silico' bulk datasets to visualize agreement between
# replicates
DoHeatmap(cluster.averages, features = rna.markers$gene, size = 3, draw.lines = FALSE)

DefaultAssay(pbmc) <- "adt.CCA"
# How can I calculate expression averages separately for each replicate?
cluster.averages <- AverageExpression(pbmc, return.seurat = TRUE,group.by = c("Time","Group"))

# You can also plot heatmaps of these 'in silico' bulk datasets to visualize agreement between
# replicates
DoHeatmap(cluster.averages, features = unique(adt.markers$gene), size = 3, draw.lines = FALSE)
```

* on un-integrated data
* per Timepoint, Group

```{r}
DefaultAssay(pbmc) <- "RNA"
# How can I calculate expression averages separately for each replicate?
cluster.averages <- AverageExpression(pbmc, return.seurat = TRUE,group.by = c("Time","Group"))

# You can also plot heatmaps of these 'in silico' bulk datasets to visualize agreement between
# replicates
DoHeatmap(cluster.averages, features = rna.markers$gene, size = 3,
    draw.lines = FALSE)

DefaultAssay(pbmc) <- "ADT"
# How can I calculate expression averages separately for each replicate?
cluster.averages <- AverageExpression(pbmc, return.seurat = TRUE,group.by = c("Time","Group"),)

# You can also plot heatmaps of these 'in silico' bulk datasets to visualize agreement between
# replicates
DoHeatmap(cluster.averages, features = unique(adt.markers$gene), size = 3,
    draw.lines = FALSE)
```

# Final data
```{r}
pbmc.final <- pbmc
```


#### Sanity check
```{r}
Idents(pbmc.final) <- "CellType_L2"

VlnPlot(object = pbmc.final, features = "CD16",assay = "ADT", split.by = 'CellType_L2',pt.size = 0.01,cols = l2.cluster.ids.colors) + NoLegend() + labs(subtitle = "Protein level")
VlnPlot(object = pbmc.final, features = "CD1C",assay = "RNA", split.by = 'CellType_L2',pt.size = 0.1,cols = l2.cluster.ids.colors) + NoLegend() + labs(subtitle = "mRNA level")
```



```{r fig.asp=0.5}
# Dot plots - the size of the dot corresponds to the percentage of cells expressing the
# feature in each cluster. The color represents the average expression level
DotPlot(pbmc.final,features = rownames(pbmc.final@assays$ADT),assay = "ADT") + RotatedAxis()
```



## Mait cell check
* markers from tobi

```{r}
mait.markers <- c("TRAV1","TRAV-2","DPP4","SLC4A10","CD161","IL18R","IL7R")
##ccr5 positiv men ccr7 negativ
tibble(genes = rownames(pbmc@assays$RNA)) %>% filter(genes %in% mait.markers)
```

```{r}
VlnPlot(object = pbmc.final, features = "IL7R", assay = "RNA", split.by = 'CellType_L2',pt.size = 0.1,cols = l2.cluster.ids.colors,ncol = 1) + NoLegend()
VlnPlot(object = pbmc.final, features = "DPP4", assay = "RNA", split.by = 'CellType_L2',pt.size = 0.1,cols = l2.cluster.ids.colors,ncol = 1) + NoLegend()

```

```{r}
FeaturePlot(subset(x = pbmc.final,
                   cells = colnames(pbmc.final)[pbmc.final@meta.data$CellType_L2 %in% c("CD8+ CD127 CD27","CD4+ mix","CD4+ T naive")]),
            reduction = "wnn.umap",
            #split.by = "Time",
            features = c("rna_CCR5","rna_CCR7",mait.markers,"rna_GZMB"),
            order = T,
            pt.size = 0.2,
            #slot = "data",
            combine = T)

VlnPlot(subset(x = pbmc.final,
               cells = colnames(pbmc.final)[pbmc.final@meta.data$CellType_L2 %in% c("CD8+ CD127 CD27","CD4+ mix","CD4+ T naive")]),
        #split.by = "Time",
        features = c("rna_CCR5","rna_CCR7",mait.markers,"rna_GZMB"),
        assay = "rna.CCA",
        split.by = 'CellType_L2',
        pt.size = 1,
        cols = l2.cluster.ids.colors,
        ncol = 5) + NoLegend()

```




```{r}
##save seurat object
#saveRDS(pbmc.final, paste0("../../data/SeuratObjects/",Sys.Date(),"AbSeq_Cell_Calling_qc_cca_wnn_clustering_annotated.rds"))
saveRDS(pbmc.final, "../../data/data/rhapsody/AbSeq_Cell_Calling_qc_cca_wnn_clustering_annotated.rds")
```
