---
  title: "Figure panles for manuscript"
author: "Julius (MJL)"
date: "`r Sys.Date()`"
output: html_document
---

# Figure Panel

## Figure 1

-   Acute Malaria

```{r Figure1, echo=FALSE, warning=FALSE,out.width='100%', message=FALSE, fig.height=9,dev = c("png","pdf")}
pdf(paste0(result.dir,"Figure_1.pdf"), width = 6.9, height = 9)#,paper = "a4",colormodel = my_pdf_colormodel) 
cohort_fig <- ggplot2::ggplot() +
  ggplot2::annotation_custom(grid::rasterGrob(png::readPNG("../doc/figs_biorender/20240222_MIPCohort_Figure1A_pil.png"),
                                              width=ggplot2::unit(3.5,"in"),
                                              height=ggplot2::unit(1.2,"in")),
                             -Inf, Inf, -Inf, Inf) + theme(rect = element_rect(fill = "transparent"))

layout <- "
AAAABC
DDEEEE
DDEEEE
FFGGGG
FFGGGG
FFHHHH
FFHHHH
"

layout <- "
AAABCD
EEFFFF
EEFFFF
GGHHHH
GGHHHH
GGIIII
GGIIII
"

## A
wrap_elements(full = cohort_fig) +
  ## B  
  wrap_elements(full = fig1.list$general_sex_age_dist + theme(legend.position = "none") + theme_a4_pdf) +
  ## C
  wrap_elements(full = fig1.list$timepoint_sex_perc + theme_a4_pdf + theme(legend.box.spacing = unit(0, "pt")) +
                                    guides(fill = guide_legend(ncol = 1))) + 

  ## D
  wrap_elements(full = fig1.list$timepoint_exposure + theme_a4_pdf + theme(legend.box.spacing = unit(0, "pt"),
                                                                           #     axis.text.y = element_blank(),
                                                                            #    axis.title.y = element_blank()
                                                                           ) +
                  guides(fill = guide_legend(ncol = 1))) + 
              
  wrap_elements(full= pca_fig1 + 
                  theme_a4_pdf + 
                  theme(legend.position = "top",
                        legend.box.spacing = unit(0, "pt"),
                        axis.text = element_blank(),
                        axis.title = element_text(size=6),
                        axis.ticks = element_blank(),
                        panel.grid.major.y = element_blank())) + 
  ## E
  wrap_elements(full = dap.acute.volcano + theme_a4_pdf) +
  
  ## F
  wrap_elements(full = grid.grabExpr(draw(acute.npx.top25.hm, merge_legend = TRUE))) +
  ## G
  wrap_elements(full = violin_malaria_top10 + theme_a4_pdf) +
  ## H
  wrap_elements(full = violin_malaria_top10_down + theme_a4_pdf) +
  
  patchwork::plot_layout(design = layout)  &
  patchwork::plot_annotation(title = "Figure 1") & #
  patchwork_panel_a4_pdf 
dev.off()
```

```{r}
png("../../../Desktop/Science - Färnert Group/PhD/Thesis/Figures/Study2_Figur1F_volcano.png",width=7,height=7,units="cm",res=300)
dap.acute.volcano + theme_a4_pdf
dev.off()
```


```{r Figure1-wo-annotation, eval=FALSE, fig.height=9, message=FALSE, warning=FALSE, dev=c("png","pdf"), include=FALSE, out.width='100%'}
pdf(paste0(result.dir,"Figure_1_old.pdf"), width = 6.9, height = 9)#,paper = "a4",colormodel = my_pdf_colormodel) 

cohort_fig <- ggplot2::ggplot() +
  ggplot2::annotation_custom(grid::rasterGrob(png::readPNG("../doc/figs_biorender/20240222_MIPCohort_Figure1A_pil.png"),
                                              width=ggplot2::unit(4,"in"),
                                              height=ggplot2::unit(1.2,"in")),
                             -Inf, Inf, -Inf, Inf) + theme(rect = element_rect(fill = "transparent"))

layout <- "
AAAABC
DDEEEE
DDEEEE
FFGGGG
FFGGGG
FFHHHH
FFHHHH
"

## A
wrap_elements(full = cohort_fig) +
  ## B  
  wrap_elements(full = fig1.list$general_sex_age_dist + theme(legend.position = "none") + theme_a4_pdf) +
  ## C
  wrap_elements(full = fig1.list$timepoint_sex_perc + theme_a4_pdf + theme(legend.box.spacing = unit(0, "pt"))) +
  ## D
  wrap_elements(full= pca_fig1 + 
                  theme_a4_pdf + 
                  theme(legend.position = "top",
                        legend.box.spacing = unit(0, "pt"),
                        axis.text = element_blank(),
                        axis.title = element_text(size=6),
                        axis.ticks = element_blank(),
                        panel.grid.major.y = element_blank())) + 
  ## E
  wrap_elements(full = dap.acute.volcano + theme_a4_pdf) +
  
  ## F
  wrap_elements(full = grid.grabExpr(draw(acute.npx.top25.hm, merge_legend = TRUE))) +
  ## G
  wrap_elements(full = violin_malaria_top10 + theme_a4_pdf) +
  ## H
  wrap_elements(full = violin_malaria_top10_down + theme_a4_pdf) +
  
  patchwork::plot_layout(design = layout)  &
  patchwork::plot_annotation(title = "Figure 1") & #
  patchwork_panel_a4_pdf 
dev.off()
```

## Related to Figure 1 - S1

-   effect on previous exposure on acute malaria

```{r Figure1-S0, echo=FALSE, warning=FALSE,out.width='100%', message=FALSE, fig.height=9,dev = c("png","pdf")}
pdf(paste0(result.dir,"Figure_1_S1.pdf"), width = 6.9, height = 6)#,paper = "a4",colormodel = my_pdf_colormodel)

layout <- "
AAA
BBC
DDD
"
layout <- "
AABB
CCBB
DDDD
"



## A
wrap_elements(full = grid.grabExpr(draw(sample_overlap_hm)))  + 
  ## B
  wrap_elements(full = acute_exposure_volcano + theme_a4_pdf +
                  theme(legend.position = c(0.8, 0.4),#"right",
                        axis.title = element_text(size=6),
                        axis.text = element_text(size=6),
                        axis.text.y = element_blank(),
                        panel.grid.major = element_blank(), 
                        panel.grid.minor = element_blank(),
                        panel.background = element_blank(),
                        axis.line = element_line(colour = "black"))) +# & theme(legend.box.spacing = unit(0, "pt"))) +
  ## C
  #acute_exposure_significant +
  ## D
  plot(euler(list("acute" = lme_res_padj %>% filter(FDR==T) %>% pull(Assay),
                  "exposure"= lme_res_expo %>% filter(FDR==T) %>% pull(Assay))),
       fills = c("#C51B7D",
                 "white"),
       quantities = TRUE,
       lty = 1,#1:3,
       fontsize=1,
       labels = list(fontsize=5),
       shape = "ellipse",adjust_labels = T) + 
  ## E
  acute_exposure_significant +
  #intersect_focus + theme_a4_pdf + 
  
  patchwork::plot_layout(design = layout) +
  patchwork::plot_annotation(title = "Supplementary Figure 1 - Related to Figure 1") &
  patchwork_panel_a4_pdf 

dev.off()
```

```{r}
acute_exposure_significant
```


## Related to Figure 1 - S2

-   Plasma proteomics after P.falciparum malaria

```{r Figure1-S1, echo=FALSE, warning=FALSE,out.width='100%', message=FALSE, fig.height=9,dev = c("png","pdf")}
pdf(paste0(result.dir,"Figure_1_S2.pdf"), width = 6.9, height = 9)#,paper = "a4",colormodel = my_pdf_colormodel)

layout <- "
AAAAAAAADDDDD
BBBBBBBBEEEEE
BBBBBBBBEEEEE
BBBBBBBBFFFFF
"

## A
wrap_elements(full = data.aov.plot + theme_a4_pdf) + 
  ## B
  wrap_elements(full = anova.panel & theme_a4_pdf & theme(legend.box.spacing = unit(0, "pt"))) +
  ## C
  wrap_elements(full = venn.DAP.acute.d10 + theme(strip.text = element_text(size=2),  plot.title.position = "plot")) + 
  ## D
  wrap_elements(full = d10_malaria_volcano + theme_a4_pdf) +
  ## E
  wrap_elements(full = acute_d10_comp +theme(legend.position="top",
                                             legend.box.spacing = unit(0, "pt"))) +
  
  patchwork::plot_layout(design = layout) +
  patchwork::plot_annotation(title = "Supplementary Figure 2 - Related to Figure 1") &
  patchwork_panel_a4_pdf 

dev.off()
```

## Related to Figure 1 - S3

-   Differential abundant proteins in acute malaria

```{r Figure1-S2, echo=FALSE, warning=FALSE,out.width='100%', message=FALSE, fig.height=6,dev = c("png","pdf")}
pdf(paste0(result.dir,"Figure_1_S3.pdf"), width = 6.9, height = 6)#,paper = "a4",colormodel = my_pdf_colormodel)

kegg.hsa04060_fig <- ggplot2::ggplot() +
  ggplot2::annotation_custom(grid::rasterGrob(png::readPNG("hsa04060.pathview.png")))#,

layout <- "
AAAAAA
BBBBBB
BBBBBB
BBBBBB
BBBBBB
"
## A
wrap_elements(full = 
                cp.kegg.acutefc1 + theme_a4_pdf + ggtitle("KEGG pathway analysis") + 
                theme(axis.ticks.x = element_blank(),
                      text = element_text(size=6)) ) +
  ## B
  wrap_elements(full= kegg.hsa04060_fig ) +
  
  patchwork::plot_layout(design = layout) +
  patchwork::plot_annotation(title = "Supplementary Figure 3 - Related to Figure 1") & 
  patchwork_panel_a4_pdf 
dev.off()
```

## Figure 2

-   Mapping of proteins to resource (HPA)

```{r Figure2, echo=FALSE, warning=FALSE,out.width='100%', message=FALSE, fig.height=5, dev = c("png","pdf")}
pdf(paste0(result.dir,"Figure_2.pdf"), width = 6.9, height = 5.5)#, paper = "a4",colormodel = my_pdf_colormodel)

layout <- "
AAAACC
BBBBCC
BBBBCC
"

## A
wrap_elements(full = hpa.protein.origin.overview + 
                theme_a4_pdf +
                theme(legend.position = "none",
                      legend.justification = c(1, 0),
                      panel.grid.major.y = element_blank()) + 
                guides(fill=guide_legend(ncol=2,byrow=TRUE)))  +
  ## B
  
  wrap_elements(full = hpa.function.bubbleplot + 
                  theme_a4_pdf + theme(legend.position="none",
                                       axis.text.x = element_text(angle=0))) + 
  ## C
  wrap_elements(full= acute_malaria_hpa_source + theme_a4_pdf + theme(legend.position="none")) + 
  
  patchwork::plot_layout(design = layout,guides = "collect") +
  patchwork::plot_annotation(title = "Figure 2") & 
  patchwork_panel_a4_pdf 

dev.off()
```



## Related to Figure 2 - S4

-   potential tissue leakage - Resource

```{r Figure2-S3,fig.height=7,dev = c("png","pdf"), out.width='100%'}
pdf(paste0(result.dir,"Figure_2_S4.pdf"), width = 6.9, height = 8)#,paper = "a4",colormodel = my_pdf_colormodel) height=7

layout <- "
AAACC
AAACC
BBBCC
BBBCC
DDDDD
EEE##
"

## A
wrap_elements(full = dap.origin.w.tl + theme_a4_pdf) +
  ## B
  wrap_elements(full = alluvial_proteinorigin + theme_a4_pdf + theme(text = element_text(size=6))) +
  ## C
  grid.grabExpr(draw(hm.tissue.leakage)) +#) + 
  ## D
  wrap_elements(full = tissue.leakage.violine + theme_a4_pdf + theme(legend.position = "none")) +
  ## E
  wrap_elements(full=agxt_hao1_alat_asat_cor + theme_a4_pdf) +
  
  patchwork::plot_layout(design = layout) +
  patchwork::plot_annotation(title = "Supplementary Figure 4 - Related to Figure 2") &
  patchwork_panel_a4_pdf 

dev.off()
```

## Related to Figure 2 - S5

-   Secreted to blood and extracellular - Resource

```{r Figure2-S4,fig.height=10,dev = c("png","pdf"), out.width='100%'}
pdf(paste0(result.dir,"Figure_2_S5.pdf"), width = 6.9, height = 10.5)#,paper = "a4",colormodel = my_pdf_colormodel)

layout <- "
AAABBB
AAABBB
AAABBB
AAACCC
AAACCC
AAADDD
AAADDD
"

## A
wrap_elements(full = acute_malaria_hpa_function_facet.list$`Secreted to blood`) +
  ## B
  wrap_elements(full = acute_malaria_hpa_function_facet.list$`Intracellular and membrane`) +
  ## C
  wrap_elements(full = acute_malaria_hpa_function_facet.list$`Secreted in other tissues`) +
  ## D
  wrap_elements(full = acute_malaria_hpa_function_facet.list$`Secreted to extracellular matrix`) +
  
  patchwork::plot_layout(design = layout) +
  patchwork::plot_annotation(title = "Supplementary Figure 5 - Related to Figure 2") &
  patchwork_panel_a4_pdf 

dev.off()
```

## Figure 3

-   Potential source and target for soluble proteins

```{r Figure3, fig.height=9, dev = c("png","pdf")}
pdf(paste0(result.dir,"Figure_3.pdf"),width = 6.9, height = 9)#,paper = "a4",colormodel = my_pdf_colormodel)

layout <- "
AAABBBBCCCC
AAABBBBCCCC
DDDDDDDDDDD
DDDDDDDDDDD
DDDDDDDDDDD
DDDDDDDDDDD
DDDDDDDDDDD
EEEEEFFFFFF
EEEEEFFFFFF
EEEEEFFFFFF
EEEEEFFFFFF
EEEEEFFFFFF
"

## A
wrap_elements(full= rhapsody_umap_ggplot_l1 + coord_fixed(ratio = 1)) + 
  ## B
  wrap_elements(full= per_sample_perc_l1 +
                  theme_a4_pdf + theme(legend.position = "top",
                                       legend.box.spacing = unit(0, "pt"),
                                       axis.text.x = element_text(size = 4),
                                       strip.text.x = element_text(size=4))) +
  ## C
  wrap_elements(full= rhapsody_umap_ggplot_l2 + coord_fixed(ratio = 1)) + 
  ## D
  wrap_elements(full = grid.grabExpr(draw(pbmc_l2_acute_hm.wide, 
                                          merge_legends = TRUE,
                                          auto_adjust = T,
                                          heatmap_legend_side="right",
                                          padding = unit(c(1, 1, 1, 1), "mm")))) +
  ## E
  wrap_elements(full= ligand_receptor_nw) +
  ## F
  wrap_elements(full = grid.grabExpr(draw(pbmc_l2_acute_cellphonedb_hm.wide,
                                          merge_legends = TRUE,
                                          heatmap_legend_side="right")) ) +
  
  patchwork::plot_layout(design = layout) +
  patchwork::plot_annotation(title = "Figure 3") & 
  patchwork_panel_a4_pdf 

dev.off()
```

## Related to Figure 3 - S6

-   Rhapsody scRNA/Ab-Seq of PBMCs from malaria patients

```{r Figure3-S5, warning=FALSE,out.width='100%', message=FALSE, fig.height=9,dev = c("png","pdf")}

pdf(paste0(result.dir,"Figure_3_S6.pdf"), width = 6.9, height = 9)#,paper = "a4",colormodel = my_pdf_colormodel)

layout <- "
AAABBBBCCC
DDDDDDDDDD
EEEEEEEEEE
EEEEEEEEEE
FFFGGGGGGG
FFFGGGGGGG
"
## A - cells per sample
wrap_elements(full= rhapsody_cells_per_sample + 
                theme(legend.position = "top",
                      axis.text.y = element_blank(),
                      legend.box.spacing = unit(0, "pt"),
                      axis.ticks.x = element_line()) + theme_a4_pdf) + 
  ## B 
  wrap_elements(full = rhapsody_umap_ggplot_int_orig.ident + 
                  theme_a4_pdf + theme(axis.text.x = element_blank(),
                                       axis.text.y = element_blank(),
                                       axis.ticks.x = element_blank(),
                                       axis.ticks.y = element_blank())) +#) + 
  ## C 
  wrap_elements(full = rhapsody_umap_ggplot_int_time + theme_a4_pdf +
                  theme(axis.text.x = element_blank(),
                        axis.text.y = element_blank(),
                        axis.ticks.x = element_blank(),
                        axis.ticks.y = element_blank())) +#) + 
  ## D
  wrap_elements(full= vln_adt.weight + theme_a4_pdf) + 
  
  ## E 
  wrap_elements(full=  dotplot.rna + 
                  theme_a4_pdf + theme(legend.position = "right") + ggtitle("mRNA")) + 
  ## F
  wrap_elements(full = cellnumbers_l2 + 
                  theme(axis.title = element_text(size=6), 
                        axis.text = element_text(size = 6))) + 
  ## G
  wrap_elements(full = genes.oi.timepoints) +
  
  patchwork::plot_layout(design = layout) +
  patchwork::plot_annotation(title = "Supplementary Figure 6 - Related to Figure 3") & 
  patchwork_panel_a4_pdf 
dev.off()
```

## Related to Figure 3 - S7

```{r Figure3-S6, fig.height=9.5, dev=c("png","pdf")}
#pdf(paste0(result.dir,"Figure_3_S6.pdf"),paper = "a4", width = 6.9, height = 10)
cairo_pdf(paste0(result.dir,"Figure_3_S7.pdf"), width = 6.9, height = 10)
layout <- "
AACCDDD
BBBBDDD
EEEEFFF
EEEEFFF
EEEEFFF
EEEEFFF
"
## A
wrap_elements(full= dooley_umap_ggplot + 
                theme_a4_pdf + theme(axis.text.x = element_blank(),
                                     axis.text.y = element_blank(),
                                     axis.ticks.x = element_blank(),
                                     axis.ticks.y = element_blank())) + 
  ## B
  wrap_elements(full= dooley_per_sample_perc + 
                  theme_a4_pdf + theme(legend.position = "none",
                                       legend.text = element_text(size=5),
                                       legend.box.spacing = unit(0, "pt"),
                                       strip.text.x = element_text(size=4)) +
                  guides(fill=guide_legend(ncol=4,byrow=TRUE))) +  
  ## C
  wrap_elements(full = dooley_0_cellnumbers + theme_a4_pdf) + 
  ## D
  wrap_elements(full = grid.grabExpr(draw(compare_dooley_rhapsody_hm_new,
                                          row_dend_side = "left",
                                          heatmap_legend_side = "right",
                                          main_heatmap = "average\ngene\nexpression",
                                          auto_adjust = T,
                                          padding = unit(c(1, 1, 1, 1), "mm")))) + 
  ## E
  wrap_elements(full= 
                  grid.grabExpr(draw(dooley_day0_hm.hpa.mapping, 
                                     merge_legends = TRUE,
                                     heatmap_legend_side = "right",
                                     annotation_legend_side = "right",
                                     padding = unit(c(-1, -1, -1, -1), "mm")))) + 
  ## F
  wrap_elements(full= grid.grabExpr(draw(dooley_day0_hm.no.hpa.mapping, 
                                         merge_legends = TRUE))) +
  
  
  
  patchwork::plot_layout(design = layout) +
  patchwork_panel_a4_pdf &
  patchwork::plot_annotation(title = "Supplementary Figure 7 - Related to Figure 3 ") 

dev.off()
```

## Figure 4

-   Patient stratification

```{r Figure4, fig.height=6.5, message=FALSE, warning=FALSE, dev=c("png","pdf")}

cairo_pdf(paste0(result.dir,"Figure_4.pdf"),  width = 6.9, height = 6.5)

layout <- "
AAACCCC
BB#CCCC
DDDCCCC
DDDEEEE
"


tmp.plot <- acute.dnpx.pca.clustered +
  theme_a4_pdf + 
  theme(legend.position = "right",
        legend.box.spacing = unit(0, "pt"),
        axis.text = element_blank(),
        axis.title = element_text(size=6),
        axis.ticks = element_blank(),
        panel.grid.major.y = element_blank())

## A
wrap_elements(full = ggExtra::ggMarginal(tmp.plot, type="density", groupColour = TRUE, groupFill = TRUE)) + 
  ##B
  wrap_elements(full = clusters_sofa + theme_a4_pdf) +
  
  ## c
  wrap_elements(full = clin.data.severity.groups.new & theme_a4_pdf + theme(strip.text.x = element_text(size = 5,face="bold"))) +
  
  ## D
  wrap_elements(full= severity_groups_conv_volc + theme_a4_pdf) +
  
  ## E
  
  ggplot2::ggplot() +
             ggplot2::annotation_custom(grid::rasterGrob(magick::image_read_pdf(paste0(result.tmp.dir,"severity_daps_upset.pdf"))[2],
                                                          width=ggplot2::unit(8,"cm"),
                                                          height=ggplot2::unit(3.5,"cm")),
                                        -Inf, Inf, -Inf, Inf) + theme(rect = element_rect(fill = "transparent")) +
  
  ## 
  patchwork::plot_layout(design = layout) +
  patchwork::plot_annotation(title = "Figure 4") & 
  patchwork_panel_a4_pdf 

dev.off()
```

## Related to Figure 4 - S8

```{r Figure4-S7, fig.height=9, message=FALSE, warning=FALSE, dev=c("png","pdf")}
cairo_pdf(paste0(result.dir,"Figure_4_S8.pdf"), width = 6.9, height = 9)

layout <- "
AAAA
AAAA
BCDD
EEE#
"

layout <- "
AABBB
AABBB
AABBB
CCCCC
CCCCC
DEFFF
GGG##
"

## A
clin_para_whole_cohort + theme_a4_pdf + theme(strip.text.x = element_text(face=NULL, size=5)) + 
  ## B
  ggplot2::ggplot() +
   ggplot2::annotation_custom(grid::rasterGrob(magick::image_read_pdf(paste0(result.tmp.dir,"chordDiagram.pdf")),
                                              width=ggplot2::unit(9.0,"cm"),
                                             height=ggplot2::unit(9.0,"cm")),
                           -Inf, Inf, -Inf, Inf) + theme(rect = element_rect(fill = "transparent")) +
  ## C
  wrap_elements(full=grid.grabExpr(draw(hm.sofa.clin,
                                        merge_legends = F,
                                        heatmap_legend_side = "bottom",
                                        annotation_legend_side = "right"))) +
  ## D
  wrap_elements(full= pca_FCmedian+ theme_a4_pdf) +
  ## E
  wrap_elements(full= acute.dnpx.ellbow + theme_a4_pdf) +
  ## F
  wrap_elements(full= grid.grabExpr(draw(pcaDF_FCmedian_PC1_6_hm))) +
  ## G
  wrap_elements(full = liver.tissueleakage.severity.plot + theme_a4_pdf + theme(legend.position = "none")) +
  
  patchwork::plot_layout(design = layout) +
  patchwork::plot_annotation(title = "Supplementary Figure 8 - Related to Figure 4") & 
  patchwork_panel_a4_pdf  

dev.off()
```

## Figure 5

```{r Figure5, fig.height=4.5, message=FALSE, warning=FALSE, dev=c("png","pdf")}
pdf(paste0(result.dir,"Figure_5.pdf"), width = 6.9, height = 4.5)#,paper = "a4",colormodel = my_pdf_colormodel) 

layout <- "
ABBCCCC
ABBCCCC
DDDDDDD
DDDDDDD
DDDDDDD
EEEEEEE
EEEEEEE
"
layout <- "
ABBCCCC
ABBCCCC
DDDDDDD
DDDDDDD
DDDDDDD
"

## A
wrap_elements(full = grid.grabExpr(draw(assay_adj_hm,
                                        heatmap_legend_side = "bottom",
                                        merge_legends = TRUE))) + 
  ## B
  wrap_elements(full = module_trait_plot + theme_a4_pdf + theme(legend.box.spacing = unit(0, "pt"))) +
  ## C
  wrap_elements(full = reactome_ora + theme_a4_pdf + 
                  theme(axis.text.x = element_text(vjust=-2),
                        legend.box.spacing = unit(0, "pt"))) +
  ## D
  wrap_elements(full = (reactome_ora_IIBLNL + 
                          reactome_ora_ND + 
                          reactome_ora_TNFR2+ 
                          guide_area() +
                          plot_layout(guides = "collect",
                                      widths = c(2,2,2,.5)))) +
  
  patchwork::plot_layout(design = layout) +
  patchwork::plot_annotation(title = "Figure 5") &
  patchwork_panel_a4_pdf 

dev.off()
```

## Related to Figure 5 - S8

```{r Figure5-S8, fig.height=4, message=FALSE, warning=FALSE, dev=c("png","pdf")}
pdf(paste0(result.dir,"Figure_5_S9.pdf"), width = 6.9, height = 4)#,paper = "a4",colormodel = my_pdf_colormodel) 

layout <- "
AB
"
## A
wrap_elements(full = module_overview + theme_a4_pdf + theme(axis.text.x = element_blank())) + 
  ## B
  wrap_elements(full = turquoise_module_restrictions_density + theme_a4_pdf) +
  
  patchwork::plot_layout(design = layout) +
  patchwork::plot_annotation(title = "Supplementary Figure 9 - Related to Figure 5") &
  patchwork_panel_a4_pdf 
dev.off()
```

## Figure 6

```{r Figure6, fig.height=5, message=FALSE, warning=FALSE, dev=c("png","pdf")}
pdf(paste0(result.dir,"Figure_6.pdf"), width = 6.9, height = 5)#,paper = "a4",colormodel = my_pdf_colormodel) 

layout <- "
AAACCCC
BBBCCCC
DEEEEEE
"

## A
wrap_elements(full = splsda.kclust.clusters.ggplot + 
                coord_fixed(ratio = 1.8) + 
                coord_cartesian(clip="off") +
                theme_a4_pdf + theme(axis.text.x = element_blank(),
                                     axis.text.y = element_blank(),
                                     axis.ticks.x = element_blank(),
                                     axis.ticks.y = element_blank()) +
                theme(legend.position = "right")) +
  ## B
  wrap_elements(full = plsda_loadings.volcano.alt + theme_a4_pdf) +
  ## C
  wrap_elements(full = splsda.c1.top9 + theme_a4_pdf +
                  theme(axis.text.x = element_blank(),
                        legend.position = "none",
                        legend.box.spacing = unit(0, "pt"))) + 
  ## D
  wrap_elements(full = MGH_covid_ssES + theme_a4_pdf) +
  ## E
  wrap_elements(full = TF_ssES_plot + theme_a4_pdf + theme(axis.text.x = element_text(size=5))) +
  
  patchwork::plot_layout(design = layout) +
  patchwork::plot_annotation(title = "Figure 6") &
  patchwork_panel_a4_pdf 

dev.off()
```

## Figure 7
```{r Figure7, fig.height=6, message=FALSE, warning=FALSE, dev=c("png","pdf")}
pdf(paste0(result.dir,"Figure_7.pdf"), width = 6.9, height = 8)#,paper = "a4",colormodel = my_pdf_colormodel) 

layout <- "
AACCCCCC
BBDDDDDE
BBDDDDDE
##DDDDDE
"
layout <- "
AACCCCCCC
BBDDDDDDD
BBDDDDDDD
EEDDDDDDD
EEDDDDDDD
FFFFFFFFF
"

## A
wrap_elements(full = 
                plot(euler(list("Differential\nabundant\nproteins\nin\nacute malaria"=selected.assays.wcna,
                "Severity associated\nproteins in plasma" = restricted_module_turquoise)),
     fills = c("white",
               "turquoise"),
     
     quantities = TRUE,
     lty = 1,#1:3,
     fontsize=6,
     labels = list(fontsize=5),
     shape = "ellipse") 
     # ggplot2::ggplot() #+
     #ggplot2::annotation_custom(grid::rasterGrob(magick::image_read_pdf(paste0(result.tmp.dir,"severity_euler.pdf")),
     #                                            width=ggplot2::unit(3.8,"cm"),
     #                                            height=ggplot2::unit(2.8,"cm")),
     #                           -Inf, Inf, -Inf, Inf) + theme(rect = element_rect(fill = "transparent"))) +
) +
  ## B
  wrap_elements(full = 
                  hpa.protein.origin.overview_severity +
                  theme_a4_pdf +
                  theme(legend.position = "none",
                        panel.grid.major.y = element_blank()) + 
                  guides(fill=guide_legend(ncol=1,byrow=TRUE)) )  +
  ## C
  wrap_elements(full = test_plot + theme_a4_pdf +
                  guides(color=guide_legend(nrow=1,byrow=TRUE)) +
                  theme(axis.text.x = element_text(colour = "black",angle=90,hjust=1,size = 2),
                        
                        legend.position = c(0, 1.1),
                        legend.justification = c("left", "top")
                  )) +
  ## D
  wrap_elements(full= ggplot2::ggplot() +
                  ggplot2::annotation_custom(grid::rasterGrob(magick::image_read_pdf(paste0(result.tmp.dir,
                                                                                            "ImmuneCell_Protein_CircosPlot_severitymodule.pdf"),
                                                                                     density = 300),
                                                              width=ggplot2::unit(12,"cm"),#8.7
                                                              height=ggplot2::unit(12,"cm")),
                                             -Inf, Inf, -Inf, Inf) + theme(rect = element_rect(fill = "transparent"))) +
  ## E
  wrap_elements(full = severity_ligand_npx + theme_a4_pdf +
                  theme(axis.text.x = element_blank(),
                        legend.position = "none",
                        legend.box.spacing = unit(0, "pt"))) + 
  ## F
  wrap_elements(full= protein_cellnum_cornet + theme(legend.key.width = unit(.3, "cm"),
                                                     legend.key.height = unit(.3,"cm"))) + 
  
  patchwork::plot_layout(design = layout) +
  patchwork::plot_annotation(title = "Figure 7") &
  patchwork_panel_a4_pdf 

dev.off()
```



# ===== Supplementary files

## Supplementary Table S2
```{r}
daps.out%>%
  write_tsv(paste0(result.dir,"Supplementary_TableS2_DifferentiallyAbundantProteins.tsv"))
```

## Supplementary Table S4
```{r}
clin.data.severity.groups.new.data %>% 
  write_tsv(paste0(result.dir,"Supplementary_TableS4_ClinicalChemistry_severity_groups.tsv"))
```

## Supplementary Table S5
```{r}
malaria.severity.siganture %>% 
  arrange(values) %>% 
  dplyr::rename(importance = values) %>% 
  write_tsv(paste0(result.dir,"Supplementary_TableS5_SeveritySignature.tsv"))
```


## Writing the supplementary data frame into an excel file
```{r}
# Table S2 - Differential Abundance Proteins (DAP) at acute malaria compared to the healthy state at 12 months after disease.
supplementary.excel <- paste0(result.dir,"SupplementaryExcelFile.xlsx")

require(openxlsx)
list_of_datasets <- list("Table S2" = daps.out,
                         "Table S4" = clin.data.severity.groups.new.data,
                         "Table S5" = malaria.severity.siganture %>% 
                           arrange(values) %>% 
                           dplyr::rename(importance = values)
                         )
write.xlsx(list_of_datasets, file = supplementary.excel)

```


# ===== Data for Shiny app

```{r}
## FoldChange data
dap.res %>% 
  transmute(Assay, 
            UniProt,
            contrast, 
            logFC,
            SE,
            conf.low = logFC-SE,
         conf.high = logFC+SE,
         p.value,
         p.adj,
         FDR) %>% 
 # dplyr::select(-data,-lme.simple.tidy) %>%
  #mutate() %>% 
  saveRDS("../Shiny_MalariaTravellerProteomics/data/MalariaExplore1536_logFC.rds")
```


```{r}
## NPX per time point summary
data.long %>% 
  inner_join(sampleTable_simple) %>% 
  group_by(Assay, Time) %>% 
  summarise(meanNPX = mean(NPX),
            medianNPX = median(NPX),
            IQR = IQR(NPX),
            FirstQuartile = quantile(NPX,probs = c(0.25)),
            ThirdQuartile = quantile(NPX,probs = c(0.75)),
            ymin   = pmax(FirstQuartile - 1.5 * IQR), # optional
            ymax   = pmin(ThirdQuartile + 1.5 * IQR),
            SD = sd(NPX),
            SE = sd(NPX)/sqrt(length((NPX)))
            ) %>% ungroup() %>% saveRDS("../Shiny_MalariaTravellerProteomics/data/MalariaExplore1536_summaries_assay_timepoint.rds")

## NPX at Acute for each severity group as summary
data.long %>% 
  inner_join(sampleTable_simple) %>% 
  filter(Time=="Acute") %>% 
  inner_join(patient_clust,by="study_id") %>% 
  group_by(Assay, severity_lab) %>% 
  summarise(meanNPX = mean(NPX),
            medianNPX = median(NPX),
            IQR = IQR(NPX),
            FirstQuartile = quantile(NPX,probs = c(0.25)),
            ThirdQuartile = quantile(NPX,probs = c(0.75)),
            ymin   = pmax(FirstQuartile - 1.5 * IQR),
            ymax   = pmin(ThirdQuartile + 1.5 * IQR)
            ) %>% ungroup() %>% saveRDS("../Shiny_MalariaTravellerProteomics/data/MalariaExplore1536_summaries_assay_severitygroup.rds")


## FoldChange with HPA
dap.res %>% 
  dplyr::select(-data,-lme.simple.tidy) %>%
  mutate(conf.low = logFC-SE,
         conf.high = logFC+SE) %>% 
  arrange(desc(abs(logFC)),desc(p.adj)) %>% 
  arrange(-logFC) %>% 
  left_join(hpa_24.0 %>% janitor::clean_names(),by=c("UniProt" = "uniprot")) %>% 
  ungroup() %>% saveRDS("../Shiny_MalariaTravellerProteomics/data/MalariaExplore1536_logFC_hpaInfo.rds")
```

